\Title

### 2020-03-16 manuscript/manuscript.tex
Start writing Discussion

>>>>

Figures~ \ref{fig:ground-survey-differences}
and~\ref{fig:airborne-survey-differences} show that all source distributions
produce accurate predictions, both for the ground and airborne survey.
The R$^2$ scores don't show significant difference, so we can only conclude
that all the source distributions are able to produce comparable predictions.
Nevertheless, the \emph{block averaged sources} make use of less sources to
produce this predictions, what would reduce the computational load needed to
fit the sources coefficients and finally compute the actual prediction.
